Capstone Movielens Report

### 2025-01-29 reports/capstone-movielens-report.Rmd
Rmd report updated.

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the^[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)] requirements, we will evaluate the RMSE score^[Rafael A. Irizarry: Introduction to Data Science, Part II, Section 23.2: Loss function]:

Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563^[R: A Language and Environment for Statistical Computing, Section 33.6.1 Matrix Factorization, @R-base]).

@@

>>>>

The goal of the project is to build a Recommendation System using a [10M version of the MovieLens dataset](http://grouplens.org/datasets/movielens/10m/).
Following the `Netflix Grand Prize Challenge` requirements`r AutoCite(bib, "NYT1MNP")`, we will evaluate the RMSE score`r AutoCite(bib, "IDS2_23-2")`:

Our goal is to achieve a value of less than 0.86490 (vs the Netflix Challenge requirement: of at least 0.8563`r AutoCite(bib, "BigChaosSln")`).

@@

[[Netflix Awards Prize Challenge](https://archive.nytimes.com/bits.blogs.nytimes.com/2009/09/21/netflix-awards-1-million-prize-and-starts-a-new-contest/)]
